Cheat Sheet for PFPL

### 2016-07-08 pfpl/draftcheatsheet.tex
Create draft version

\end{tabular}
\end{document}

>>>>

\subsection*{XII. Control Flow}
\subsubsection*{28 Control Stacks}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

65& 258 & $\epsilon$ & Epsilon & Empty frame & Empty frame\\
66& 258 & (\textemdash) & Frame hole & Frame hole & A place to put an evaluated expression into a frame\\
67& 258 & $k;f$ & Stack with frame & Stack $k$ with frame $f$  & Stack $k$ has frame $f$ at the bottom\\
68& 258 & $\vartriangleright$ & Right triangle & Evaluate and push & Evaluate an expression and push the result into a stack frame \\
69& 258 & $\vartriangleleft$ & Left triangle & Push & Push evaluated result into a frame\\
70& 259 & $\vartriangleleft:\tau$ & Triangle colon & Push expression of type $\tau$ & Push expression of type $\tau$\\
71& 259 & $f:\tau\rightsquigarrow\tau'$ & Squiggle arrow & Transform & Frame $f$ transforms expression of type $\tau$ into expression of type $\tau'$\\
72& 261 & $s \looparrowright e$ & Loop arrow & Unravel & State $s$ goes to expression $e$ \\
73& 261 & $k \bowtie e = e'$ & Bowtie & Goes to & Stack $k$ and expression $e$ goes to expression $e'$\\

\end{document}
